---
title: "In Class Ex 11"
author: "Shreyansh Shivam"
date: "4/4/2020"
output: html_document
---

# Install Packages
```{r}
packages = c('igraph', 'tidygraph', 'visNetwork', 'lubridate', 'tidyverse')

for(p in packages){library
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```
```{r}
# Code to check if the packages are installed or not
p <- c('igraph', 'tidygraph', 'ggraph', 'visNetwork', 'lubridate', 'tidyverse')
lapply(p, require, character.only = TRUE)
```

# Importing network data from files

```{r}
GAStech_nodes <- read_csv("data/GAStech_email_node.csv")
GAStech_edges <- read_csv("data/GAStech_email_edge-v2.csv")
```
```{r}
glimpse(GAStech_edges)
```

```{r}
GAStech_edges$SentDate  = dmy(GAStech_edges$SentDate) # the sent date field to set as date from character 
GAStech_edges$Weekday = wday(GAStech_edges$SentDate, label = TRUE, abbr = FALSE)
```

# Wrangling attributes

A close examination of GAStech_edges data.frame reveals that it consists of individual e-mail flow records. This is not very useful for visualisation. In this section, we will aggregate the individual by date, senders, receivers, main subject and day of the week.

To accomplish the task, the code chunks below will be used.

```{r}
GAStech_edges_aggregated <- GAStech_edges %>%
  filter(MainSubject == "Work related") %>%
  group_by(source, target, Weekday) %>%
    summarise(Weight = n()) %>%   # summarise by the number of count
  filter(source!=target) %>%
  filter(Weight > 1) %>% # to view connectivity with at least 2 nodes
  ungroup()
GAStech_edges_aggregated
```
```{r}
GAStech_graph <- tbl_graph(nodes = GAStech_nodes, edges = GAStech_edges_aggregated, directed = TRUE)
GAStech_graph
```
```{r}
GAStech_graph %>%
  activate(edges) %>%
  arrange(desc(Weight)) # sorting of the edges as per the weight
```

```{r}
library('ggraph')
library('farver')
ggraph(GAStech_graph) +
  geom_edge_link() +
  geom_node_point()
```
```{r}
g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes()) +
  geom_node_point(aes())

g + theme_graph()
```
```{r}
g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes(colour = 'grey50')) +
  geom_node_point(aes(colour = 'grey40'))

g + theme_graph(background = 'grey10', text_colour = 'white')
```
```{r}
g <- ggraph(GAStech_graph, layout = "nicely") + 
  geom_edge_link(aes()) +
  geom_node_point(aes(colour = Department, size = 3))

g + theme_graph()
```
```{r}
g <- ggraph(GAStech_graph, layout = "nicely") + 
  geom_edge_link(aes(width=Weight), alpha=0.2) +
  scale_edge_width(range = c(0.1, 5)) +
  geom_node_point(aes(colour = Department), size = 3)

g + theme_graph()
```
```{r}
set_graph_style()

g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes()) +
  geom_node_point(aes(colour = Department))
  
g + facet_edges(~Weekday)
```

```{r}
set_graph_style()

g <- ggraph(GAStech_graph) + 
  geom_edge_link(aes()) +
  geom_node_point(aes(colour = Department))
  
g + facet_nodes(~Department)+
  th_foreground(foreground = "grey80",  border = TRUE)
```
```{r}
g <- GAStech_graph %>%
  mutate(betweenness_centrality = centrality_betweenness()) %>%
  mutate(closeness_centrality = centrality_closeness()) %>%
  ggraph(layout = "nicely") + 
  geom_edge_link(aes()) +
  geom_node_point(aes(colour = closeness_centrality, size=betweenness_centrality))

g + theme_graph()
```

```{r}
GAStech_edges_aggregated <- GAStech_edges %>%
  left_join(GAStech_nodes, by = c("sourceLabel" = "label")) %>%
  rename(from = id) %>%
  left_join(GAStech_nodes, by = c("targetLabel" = "label")) %>%
  rename(to = id) %>%
  filter(MainSubject == "Work related") %>%
  group_by(from, to) %>%
    summarise(weight = n()) %>%
  filter(from!=to) %>%
  filter(weight > 1) %>%
  ungroup()
visNetwork(GAStech_nodes, GAStech_edges_aggregated)
```
```{r}
visNetwork(GAStech_nodes, GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr")
```
```{r}
GAStech_nodes <- GAStech_nodes %>%
  rename(group = Department)
```

```{r}
visNetwork(GAStech_nodes, GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr") 
```
```{r}
visNetwork(GAStech_nodes, GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visEdges(arrows = "to", smooth = list(enabled = TRUE, type = "curvedCW"))
```
```{r}
visNetwork(GAStech_nodes, GAStech_edges_aggregated) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE)

```

